Multisensor Architecture for an Intersection Management System

### 2018-08-01 ch3-arch_sys.tex
Ch3 ok. Update.

In addition to .imscfg file, there are different types of messages and parameters which have its own structure, for example used for sensors configuration or processed data. The table \ref{desc_map} gives a description of the types of information used. A more detailed documentation is given in appendix TODO.

@@

@@

\item[vehicle\_counter] \hfill

@@

This block accepts different types of inputs, cluster\_msg and occgrid\_msg. It process the incoming data, and generate bounding boxes based on the clusters or based on the occupancy grid, according to the input. Having these bounding boxes, which represent detected vehicles, scene configuration data is loaded and the geometric parameters of the legs and lanes are used to generate virtual sensors at the entry and exit points of the intersection and check the overlaping of detected vehicles with aforemetioned virtual sensors.

This detection is made in a frame basis, meaning that if the overlaping area of a virtual sensor is greater than a threshold $ov_{th}$, it is considered that there is a vehicle over the sensor in that frame. Thus, the vehicle counter $v_{cnt}$ is incremented by one when a transition from occupied state to empty state is detected in a new frame.

%\item[clusters\_to\_occupancy\_level] \hfill
%\begin{figure}[ht!]
%\centering
%\includegraphics[scale=1]{fig/3/clusters2occlvl.pdf}
%\caption{clusters\_to\_occupancy\_level}
%\label{clusters_to_occupancy_level}
%\end{figure}

%\item[occgrid\_vehicle\_counter] \hfill
%
%\begin{figure}[ht!]
%\centering
%\includegraphics[scale=1]{fig/3/occgrid_veh_counter.pdf}
%\caption{occgrid\_vehicle\_counter}
%\label{occgrid_vehicle_counter}
%\end{figure}

%\item[occgrid\_to\_occupancy\_level] \hfill
%\begin{figure}[ht!]
%\centering
%\includegraphics[scale=1]{fig/3/occgrid2occlvl.pdf}
%\caption{occgrid\_to\_occupancy\_level}
%\label{occgrid_to_occupancy_level}
%\end{figure}

@@

\subsubsection{Situation Assesment}
\begin{description}

\item[vehicle\_counter\_merge] \hfill
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/veh_cnt_merge.pdf}
\caption{vehicle\_counter\_merge}
\label{vehicle_counter_merge}
\end{figure}
%
%\item[occupancy\_level\_merge] \hfill
%\begin{figure}[ht!]
%\centering
%\includegraphics[scale=1]{fig/3/occlvl_merge.pdf}
%\caption{occupancy\_level\_merge}
%\label{occupancy_level_merge}
%\end{figure}

>>>>

In addition to .imscfg file, there are different types of messages and parameters which have its own structure, for example used for sensors configuration or processed data. The table \ref{desc_map} gives a description of the types of information used.
% A more detailed documentation is given in appendix TODO.

@@

\todo{Finish table}

@@

\item[virtual\_sensor\_occupancy] \hfill

@@

This block accepts different types of inputs, cluster\_msg and occgrid\_msg. It process the incoming data, and generate bounding boxes based on the clusters or based on the occupancy grid, according to the input. Having these bounding boxes, which represent detected vehicles, scene configuration data is loaded and the geometric parameters of the legs and lanes are used to generate virtual sensors at the entry and exit points of the intersection and check the overlaping of detected vehicles with aforemetioned virtual sensors. The output generated by this block is the occupancy percentage of the virtual sensor, represented as a message of type vsens\_occ\_msg.
%vehicle counter $v_{cnt}$ is incremented by one when a transition from occupied state to empty state is detected in a new frame.

\begin{description}

\item[virtual\_sensor\_merge] \hfill
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/veh_cnt_merge.pdf}
\caption{virtual\_sensor\_merge}
\label{virtual_sensor_merge}
\end{figure}

This block is intended to take as inputs different messages of type vsens\_occ\_msg and merging them to increase the reliabilty of detection. First, a moving average is calculated over each input to reduce the effect of false positives or false negatives in a single frame. After this, the inputs are merged by a defined method like average, weighted average, maximum or minimum. Then, a new vsens\_occ\_msg message is dispatched as output.

@@

\subsubsection{Situation Assesment}

\item[virtual\_sensor\_to\_flow\_status] \hfill
\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/veh_cnt_merge.pdf}
\caption{virtual\_sensor\_to\_flow\_statu}
\label{virtual_sensor_to_flow_status}
\end{figure}

When a message of type vsens\_occ\_msg arrives, it is evaluated using a threshold $vo_{th}$, if the occupancy percentage of a virtual sensor is greater than $vo_{th}$, it is considered that there is a vehicle over the sensor in that frame, this is defined as occupied state. This detection is made in a frame basis, thus, a vehicle counter $v_{cnt}$ is incremented by one when a transition from occupied state to empty state is detected in a new frame.

Then, a time interval $t_{c}$ is defined for calculating the flow rate $v_{r}$. Defined as the number of transitions during that interval divided by $t_{c}$. Then, if $v_{r}$ is above a flow threshold $f_{th}$, it is considered that the traffic is flowing. Otherwise, traffic is considered stopped.
